Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-07-09 Report/dual_approach.tex
tempversion

Let  \me{\mbfa{\zeta}^{\set{b_k}}} be the locally maintained vector formed by stacking the interference entries relevant to the \ac{BS} \me{b_k}. Let \me{\mbfa{\zeta}} be the global interference entries of all \acp{BS} in the set \me{\mc{B}} stacked as a vector as
\begin{IEEEeqnarray}{rCl}
\mbfa{\zeta} &=& \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1},  \right. \nonumber \\
&\quad& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \IEEEyessubnumber \\
n_{b_k} &=& |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\mbfa{\zeta}(b_k)} denote the entries corresponding to the \ac{BS} \me{b_k} and the vector \me{\mbfa{\nu}^{\set{b_k}}} stacks the dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)}. The equality constraint for the local and the global interference vector \me{\zeta^{\set{b_k}}_{l,k,n,b} = \zeta_{l,k,n,b}, \fall b \in \bar{\mc{B}}_{b_k}, k \in \mc{U}} and \me{\forall k \in \bar{\mc{U}}_{b_k}, b=b_k} is relaxed by the partial Lagrangian in the objective as
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-2} \label{eqn-dual-1}
\underset{\substack{\gamma_{l,k,n}, \nu^{\set{b_k}}_{l,k,n,b} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}, \zeta^{\set{b_k}}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}}T} \left ( \mbfa{\zeta}^{\set{b_k}} - \mbfa{\zeta}(b_k) \right ) \IEEEyessubnumber \label{eqn-dual-2a} \\
\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta^{\set{b_k}}_{l,k,n,b} \; + \; N_0 \IEEEyessubnumber \label{eqn-dual-1d} \\
&& \zeta^{\set{b_k}}_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-dual-1e} \\
&\quad& \mbfa{\nu}^{\set{b_k}} \in \mathbb{R}^{n_{b_k}}_+, \; \eqref{eqn-8} \; \text{and} \; \eqref{eqn-primal-1c}. \IEEEyessubnumber \label{eqn-dual-1f}
\end{IEEEeqnarray}
It can be seen from the objective \eqref{eqn-dual-2a} that the global interference \me{\mbfa{\zeta}(b_k)} can be dropped from the objective \eqref{eqn-dual-2a} without affecting the optimal solution, since it is constant for the subproblems. The problem defined in \eqref{eqn-dual-2} can be decoupled to solve for the precoders at each \ac{BS} by using interference vector \me{\mbfa{\zeta}^{\set{b_k}}} as an optimization variable for the fixed interference price (dual variable) \me{\mbfa{\nu}^{\set{b_k}}}. In the current work, we consider the robust counterpart of the \acl{DD} scheme, namely \ac{ADMM} approach, which doesn't require any assumptions on the convexity of the functions for convergence \cite{boyd2011distributed}.

>>>>

Let  \me{\mbfa{\zeta}^{\set{b_k}}} be the locally maintained vector formed by stacking the interference entries relevant to the \ac{BS} \me{b_k}. Let \me{\mbfa{\zeta}} be the global interference entries of all \acp{BS} in the set \me{\mc{B}} stacked as a vector as
\begin{IEEEeqnarray}{rCl}
\mbfa{\zeta} &=& \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1},  \right. \nonumber \\
&\quad& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \IEEEyessubnumber \\
n_{b_k} &=& |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\mbfa{\zeta}(b_k)} denote the entries corresponding to the \ac{BS} \me{b_k} and the vector \me{\mbfa{\nu}^{\set{b_k}}} stacks the dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)}. The equality constraint for the local and the global interference vector \me{\zeta^{\set{b_k}}_{l,k,n,b} = \zeta_{l,k,n,b}, \fall b \in \bar{\mc{B}}_{b_k}, k \in \mc{U}} and \me{\forall k \in \bar{\mc{U}}_{b_k}, b=b_k} is relaxed by the partial Lagrangian in the objective as
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-2} \label{eqn-dual-1}
\underset{\substack{\gamma_{l,k,n}, \nu^{\set{b_k}}_{l,k,n,b} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}, \zeta^{\set{b_k}}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}}T} \left ( \mbfa{\zeta}^{\set{b_k}} - \mbfa{\zeta}(b_k) \right ) \IEEEyessubnumber \label{eqn-dual-2a} \\
\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta^{\set{b_k}}_{l,k,n,b} \; + \; N_0 \IEEEyessubnumber \label{eqn-dual-1d} \\
&& \zeta^{\set{b_k}}_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-dual-1e} \\
&\quad& \mbfa{\nu}^{\set{b_k}} \in \mathbb{R}^{n_{b_k}}_+, \; \eqref{eqn-8} \; \text{and} \; \eqref{eqn-primal-1c}. \IEEEyessubnumber \label{eqn-dual-1f}
\end{IEEEeqnarray}
In \eqref{eqn-dual-2a}, the global interference variable \me{\mbfa{\zeta}(b_k)} is dropped without affecting the optimal solution, since it is fixed for a given iteration. The problem defined in \eqref{eqn-dual-2} can be decoupled to solve for the precoders at each \ac{BS} by using interference vector \me{\mbfa{\zeta}^{\set{b_k}}} as an optimization variable for the fixed interference price (dual variable) \me{\mbfa{\nu}^{\set{b_k}}}. In the current work, we consider the robust counterpart of the \acl{DD} scheme, namely \ac{ADMM} approach, which doesn't require any assumptions on the convexity of the functions for convergence \cite{boyd2011distributed}.

### 2014-07-09 Report/kkt_mse_approach.tex
tempversion

When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} poses a nonconvex constraint, which then makes the problem difficult to solve in an iterative manner. But, in our formulation, since the rate constraint imposed by the number of queued packets waiting for the transmission in in the objective function, it provides an efficient apporach to solve the problem with the rate constraints. In this section, we provide an iterative precoder design for the \ac{JSFRA} formulation approached via \ac{MSE} reformulation as discussed in \ref{sec-3.3}. Even though the \ac{JSFRA} scheme using \ac{SCA} approach and the \ac{MSE} reformulation approach obtained the solutions by relaxing the nonconvex constraints by the half spaces, the structure of the \ac{MSE} reformulation problem allows us to decouple the problem readily without further approximations.

In order to come up with the iterative solution, we need to find the \ac{KKT} equations for the the \ac{MSE} reformulation problem defined in \eqref{eqn-mse-2}. It can be seen that the objective function \eqref{eqn-mse-2.1} has the norm function, which requires the sum of absolute values of the vector entries raised to the power \me{q}. Since the absolute of a function is not differentiable, the problem is usually solved by the subgradient approach. Since the subgradients are not unique and the selection of a subgradient and a step size are not guaranteed to be optimal, in this approach, we drop the absolute value operation for the queue deviation function so as to obtain a unique supporting vector. It is valid in the following special cases without affecting the optimal solution
\begin{itemize}
\item when the exponent \me{q} is even or,
\item when the number of backlogged packets for each user is larger than the available resources for the transmission \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}.
\end{itemize}
The first condition is required for the iterative design, since the objective function needs to be differentiable to find the \ac{KKT} equations. So, when the exponent \me{q} is even, the absolute operator can be dropped from the objective function without any change in the optimal solution for any number of queued packets.

>>>>

When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} poses a nonconvex constraint, which makes the problem difficult to solve in an iterative approach. But, in the current method, the rate constraints imposed by the number of queued packets are implicitly present in the objective function, it eliminates the need of an additional rate constraints. The current formulation uses the \ac{MSE} approach to obtain the iterative algorithm for special scenarios due to the absolute operator in the objective function. Since the absolute of a function is not differentiable, the problem is usually solved by the subgradient approach. In order to solve the problem using the closed form equations, we drop the absolute value operator in the objective to obtain the differentiable equivalent. It is valid for the following two special cases, namely, 
\begin{itemize}
\item when the exponent \me{q} is even or,
\item when the number of backlogged packets for each user is larger than the available resources for the transmission \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}.
\end{itemize}
The first condition is required for the iterative design, since the objective function needs to be differentiable to find the \ac{KKT} equations. So, when the exponent \me{q} is even, the absolute operator can be dropped from the objective function without any change in the optimal solution for any number of queued packets.
